Augmentation of a Historical Harpsichord Keyboard Replica for Haptic-Enabled Interaction in Museum Exhibitions

### 2025-02-05 src/article.tex
fix #25

\begin{figure*}
\centering
\includegraphics[width=0.8\linewidth]{src/images/details.jpg}
\caption{Details of the replica, including the key slots and sides, keys, and jacks with seagull plectra.}
\label{fig:details}
\end{figure*}

@@

\begin{figure}[!b]  
  \centering
  \includegraphics[width=\linewidth,trim={0 0 0 0.5cm},clip]{src/images/tagging-jacks-3.jpg} 
  \caption{Gradient stickers applied to the side of the jack body. The coarse gradient scale was selected to maximise signal excursion while preserving signal readout stability.}
  \Description{} 
  \label{fig:jack-tags}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{src/images/49-key-bottom-sensors-no-keys.jpg} 
  \caption{Underside of the full model keyboard, showing two chambers: the front chamber (top) and the rear chamber (bottom).} 
  \Description{} 
  \label{fig:49-key-bottom}
\end{figure}

@@

    \begin{subfigure}[h]{0.4\linewidth}
        \centering
        \includesvg[inkscapelatex=false, width = \linewidth]{images/49-key_outline}        
        \caption{rectangular shape}
        \label{fig:rect-harp}
    \end{subfigure}
    \caption{Logarithmic shape of an original \anon{Trasuntino} harpsichord contrast with the rectangular shape of the replica}    
    \Description{}
    \label{fig:log-harp-comp}
\end{figure}

@@

\begin{figure}[!t]
    \centering    
    \includegraphics[width=\linewidth]{src/images/3-key-side.png}
    \caption{
    3-Key Model Harpsichord Mechanism    
    %acquired from \anon{San Colombano, Bologna}, 2023.
    }
    \label{fig:3key}
\end{figure}

@@

\begin{figure}[!b] 
  \centering
  \includegraphics[width=0.7\linewidth,trim={0 0.5cm 0 0.5cm},clip]{src/images/simple-schematic-bw-.jpg} 
  \caption{Optical sensor in a simple voltage divider circuit. \texttt{V\_OUT} is routed to one of 8 channels on the CD4051BE multiplexer.}
  \Description{} 
  \label{fig:simple-schematic}
\end{figure}

@@

\begin{figure*}
    \centering
    \includegraphics[width=\linewidth]{src/images/block-diagram-2.pdf}
    \caption{Block diagram of PCB connections. A separate sensor signal is routed to the Arduino. LED and multiplexer (MUX) controls signal are daisy-chained through each sensor PCB.}
    \label{fig:system-block-diagram}
\end{figure*}

@@

\begin{figure}[!t]
    \centering
    \includegraphics[width=0.8\linewidth,trim={0 2cm 0 2.5cm},clip]{src/images/baffles.png}
    \caption{Baffles designed to prevent cross-talk between adjacent sensors.}
    \Description{}
    \label{fig:baffles}
\end{figure}

@@

\begin{figure}[!b] 
  \centering
  \includegraphics[width=\linewidth,trim={0 1.5cm 0 1.5cm},clip]{src/images/sensor-board-w-baffles.jpeg}
    \\
  \includegraphics[width=\linewidth]{src/images/sensor-board-reverse-side-anon.png} 
  \caption{Sensor board showing the sensor side (top) and rear side with RGB LEDs and terminal connections (bottom). The \texttt{SIG} terminal (Top Left) is routed to an ADC channel. Power \texttt{5V, 3V, GND}, multiplexer channels \texttt{A, B, C} and LED PWM input \texttt{DI} and output \texttt{DO}  connect from the previous sensor board (Left) and are routed to the next (Right).}
  \Description{} 
  \label{fig:sensor-reverse}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.8\linewidth,trim={0 5cm 0 0},clip]{src/images/mac-mini.jpg}
    \caption{Components and cabling hidden in the bottom section of the instrument case.}
    \label{fig:mac-mini}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width = \linewidth]{src/images/keyboardMuseum.JPEG}
\caption{The keyboard installed in the \emph{Oratory} at \anon{San Colombano}, and a user wearing headphones playing it.}
\label{fig:oratory}
\end{figure}

>>>>

\begin{figure*}
\centering
\includegraphics[width=0.8\linewidth]{src/images/details.jpg}
\caption{Details of the replica, including the key slots and sides, keys, and jacks with seagull plectra.}
\Description{4 images contain details of the jack rows. A large image shows the end of the jack rows where an extrusion is put to allow jack rows to be disengaged. The smaller images show the keys and jack removed from the harpsichord exposing the materials from which they are constructed. Shown also is the shims for the jack which stop it from easily sliding.}
\label{fig:details}
\end{figure*}

@@

\begin{figure}[!b]  
  \centering
  \includegraphics[width=\linewidth,trim={0 0 0 0.5cm},clip]{src/images/tagging-jacks-3.jpg} 
  \caption{Gradient stickers applied to the side of the jack body. The coarse gradient scale was selected to maximise signal excursion while preserving signal readout stability.}
  \Description{Close of two jacks with gradient stickers applied to each. Both jack lie on top of the vinyl sheet that was used for printing. The gradient is a long black bar that terminates in 7 rectangles of grey over an 8mm span. The remainder of the sticker is white. The jacks have the numbers 46 and 49 written on them at different offset illustrating the numbering system to identify their position along the keyboard.} 
  \label{fig:jack-tags}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{src/images/49-key-bottom-sensors-no-keys.jpg} 
  \caption{Underside of the full model keyboard, showing two chambers: the front chamber (top) and the rear chamber (bottom).} 
  \Description{Underside view of the models with keys removed. A cross brace split the case into four quadrants the top two are the front chambe and the bottom are the rea chamber. Visible inside are the PCB which are connected to each other with multicoloured ribbon cable. From the right 2 long cables, one for sensor signals the other for LED and multiplexer signals. Both sets of cables terinate at the controller board. The PCBs are attached with white plastic supports to the underside of the wrest plank, a thick block of wood in which the tuning pegs are screwed.} 
  \label{fig:49-key-bottom}
\end{figure}

@@

    \begin{subfigure}[h]{0.4\linewidth}
        \centering
        \includesvg[inkscapelatex=false, width = \linewidth]{images/49-key_outline}        
        \caption{rectangular shape}
        \label{fig:rect-harp}
    \end{subfigure}
    \caption{Logarithmic shape of an original \anon{Trasuntino} harpsichord contrast with the rectangular shape of the replica}    
    \Description{Line drawing of two harpsichord shapes. The top line drawing shows the longer tapering form of a full scale instrument if it had the same key layout as the replica. The second line drawing is of the replica harpsichord. The line drawing share the same scale and it can be seen that the replica is roughly one quarter the depth of a full scale instrument.}
    \label{fig:log-harp-comp}
\end{figure}

@@

\begin{figure}[!t]
    \centering    
    \includegraphics[width=\linewidth]{src/images/3-key-side.png}
    \caption{
    3-Key Model Harpsichord Mechanism    
    %acquired from \anon{San Colombano, Bologna}, 2023.
    }
    \Description{Side view of a small model mechanism of a harpsichord. The model is cut as though it were a cross section of a harpsichord mechanism. The Instrument is not to scale and only has a small sound board. Visible are the pivots through which the keys are mounted and how the two sets of jack rest on the end of the key.}
    \label{fig:3key}
\end{figure}

@@

\begin{figure}[!b] 
  \centering
  \includegraphics[width=0.7\linewidth,trim={0 0.5cm 0 0.5cm},clip]{src/images/simple-schematic-bw-.jpg} 
  \caption{Optical sensor in a simple voltage divider circuit. \texttt{V\_OUT} is routed to one of 8 channels on the CD4051BE multiplexer.}
  \Description{A circuit diagram of a voltage divider circuit. The Image shows a 100 ohm resistor in line with the LED and a 10 thousand ohm resistor connected to the emitter of the phototransistor and the collector connected to ground. The line to the bisects before the 10 thousand ohm resistor to a label titled V OUT. Arrows from the LED illustrate how light controls the base of the phototransistor.} 
  \label{fig:simple-schematic}
\end{figure}

@@

\begin{figure*}
    \centering
    \includegraphics[width=\linewidth]{src/images/block-diagram-2.pdf}
    \caption{Block diagram of PCB connections. A separate sensor signal is routed to the Arduino. LED and multiplexer (MUX) controls signal are daisy-chained through each sensor PCB.}
    \Description{The block diagram shows seven blocks each with sensor board written on them. Each sensor block has a solid arrow which connects to a block labelled Arduino Nano 33 BLE. A dashed arrow is drawn from the Ardnuino Nano 33 BLE box and travels through each sensors board. A legend shows th soldi line represnts the flow of the sensor signal and the dashed arrow the flow of LED an multiplexer control signals. Angled arrows from the sensor board point towards and away from a hatched lined representing the surface of the jacks, which illustartes the reflection of light. Lines from boxes labelled FRAM and Rotary Encoder point to and from the box labelled Arduino Nano 33 BLE.}
    \label{fig:system-block-diagram}
\end{figure*}

@@

\begin{figure}[!t]
    \centering
    \includegraphics[width=0.8\linewidth,trim={0 2cm 0 2.5cm},clip]{src/images/baffles.png}
    \caption{Baffles designed to prevent cross-talk between adjacent sensors.}
    \Description{A 3D model of the baffles used to reduce light leakage. Two slots are on the left and right sides. Two holes are visible beside each slot, through which the baffles can be attached to the PCB. A rectangular cutaway is visible for the multiplexer chip. The baffles contained14 angled extrusions 2 for each sensor.}
    \label{fig:baffles}
\end{figure}

@@

\begin{figure}[!b] 
  \centering
  \includegraphics[width=\linewidth,trim={0 1.5cm 0 1.5cm},clip]{src/images/sensor-board-w-baffles.jpeg}
    \\
  \includegraphics[width=\linewidth]{src/images/sensor-board-reverse-side-anon.png} 
  \caption{Sensor board showing the sensor side (top) and rear side with RGB LEDs and terminal connections (bottom). The \texttt{SIG} terminal (Top Left) is routed to an ADC channel. Power \texttt{5V, 3V, GND}, multiplexer channels \texttt{A, B, C} and LED PWM input \texttt{DI} and output \texttt{DO}  connect from the previous sensor board (Left) and are routed to the next (Right).}
  \Description{Two images one of the front and one of the rear of a single sensor board. The top image shows the baffles in place and how they enclose the field of view of each sensor. The bottom image shows the wires from neighbouring circuit boards terminating and the line of 7 RGB LEDs in the same spacing as the LEDs.} 
  \label{fig:sensor-reverse}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.8\linewidth,trim={0 5cm 0 0},clip]{src/images/mac-mini.jpg}
    \caption{Components and cabling hidden in the bottom section of the instrument case.}
    \Description{The mac mini and its display fitted in a shallow draw with a channel drilled in the end through which cables can be connected. The draw has dividers in place to separate the mac mini from the display.}
    \label{fig:mac-mini}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width = \linewidth]{src/images/keyboardMuseum.JPEG}
\caption{The keyboard installed in the \emph{Oratory} at \anon{San Colombano}, and a user wearing headphones playing it.}
\Description{2 images on showing the keyboard in situ in the museum and the second a user playing the keyboard. The harpsichord placed on top the drawer in which the mac mini and display reside. The whole harpsichord unit is positioned on a table. The right image shows a user standing playing the keyboard with a display for the exhibition visible in the background.}
\label{fig:oratory}
\end{figure}

### 2025-02-05 src/main.tex
fix #25

%%
%% This is file `sample-nime-paper.tex',
%% generated with the docstrip utility.
%%
%% The original source files were:
%%
%% samples.dtx  (with options: `all,proceedings,bibtex,sigconf')
%% 
%% IMPORTANT NOTICE:
%% 
%% For the copyright see the source file.
%% 
%% Any modified versions of this file must be renamed
%% with new filenames distinct from sample-nime-paper.tex.
%% 
%% For distribution of the original source see the terms
%% for copying and modification in the file samples.dtx.
%% 
%% This generated file may be distributed as long as the
%% original source files, as listed above, are part of the
%% same distribution. (The sources need not necessarily be
%% in the same archive or directory.)
%%
%%
%% Commands for TeXCount
%TC:macro \cite [option:text,text]
%TC:macro \citep [option:text,text]
%TC:macro \citet [option:text,text]
%TC:envir table 0 1
%TC:envir table* 0 1
%TC:envir tabular [ignore] word
%TC:envir displaymath 0 word
%TC:envir math 0 word
%TC:envir comment 0 0
%%
%%
%% History of NIME Template Updaters:
%% Modified by Florent Berthaut, Charles Martin, Yichen Wang, 21 November 2024
%% Modified by Adnan Marquez-Borbon 30 November 2022
%% Modified by Courtney Reed 28 November 2022
%% Modified by Joe Wright 14 December 2019
%% Modified by Niccolò Granieri 10 October 2018
%% Modified by Angelo Fraietta 23 December 2018
%% Modified by Angelo Fraietta 22 November 2018
%% Modified by Rodrigo Schramm on 22 September 2018
%% Modified by Luke Dahl on 17 October 2-17
%% Modified by Cumhur Erkut on <2016-10-11 Tue>
%% Modified by Edgar Berdahl on 5 November 2014
%% Modified by Baptiste Caramiaux on 25 November 2013
%% Modified by Kyogu Lee on 7 October 2012
%% Modified by Georg Essl on 7 November 2011
%%
%% And here's the template:
%%
%% The first command in your LaTeX source must be the \documentclass
%% command.
%%
%% For submission and review of your manuscript please change the
%% command to \documentclass[manuscript, screen, review]{nimeart}.
%%
%% When submitting camera ready or to TAPS, please change the command
%% to \documentclass[sigconf]{nimeart} or whichever template is required
%% for your publication.
%%
%%
% \documentclass[sigconf]{nimeart}
\documentclass[sigconf]{nimeart}
% \documentclass[sigconf,anonymous,review]{nimeart}
\usepackage{graphicx,subcaption,svg}

@@

% Option 2:
\begin{teaserfigure}
 \centering
  \includegraphics[width=0.58\textwidth]{src/images/49-key-front-top.png}
  \caption{49-key Model Harpsichord Mechanism by \anon{Roberto Livi, Bologna 2024}}
  \Description{49-key Model Harpsichord Mechanism by \anon{Roberto Livi, Bologna 2024}}
  \label{fig:teaser}
\end{teaserfigure}

>>>>

%%
%% This is file `sample-nime-paper.tex',
%% generated with the docstrip utility.
%%
%% The original source files were:
%%
%% samples.dtx  (with options: `all,proceedings,bibtex,sigconf')
%% 
%% IMPORTANT NOTICE:
%% 
%% For the copyright see the source file.
%% 
%% Any modified versions of this file must be renamed
%% with new filenames distinct from sample-nime-paper.tex.
%% 
%% For distribution of the original source see the terms
%% for copying and modification in the file samples.dtx.
%% 
%% This generated file may be distributed as long as the
%% original source files, as listed above, are part of the
%% same distribution. (The sources need not necessarily be
%% in the same archive or directory.)
%%
%%
%% Commands for TeXCount
%TC:macro \cite [option:text,text]
%TC:macro \citep [option:text,text]
%TC:macro \citet [option:text,text]
%TC:envir table 0 1
%TC:envir table* 0 1
%TC:envir tabular [ignore] word
%TC:envir displaymath 0 word
%TC:envir math 0 word
%TC:envir comment 0 0
%%
%%
%% History of NIME Template Updaters:
%% Modified by Florent Berthaut, Charles Martin, Yichen Wang, 21 November 2024
%% Modified by Adnan Marquez-Borbon 30 November 2022
%% Modified by Courtney Reed 28 November 2022
%% Modified by Joe Wright 14 December 2019
%% Modified by Niccolò Granieri 10 October 2018
%% Modified by Angelo Fraietta 23 December 2018
%% Modified by Angelo Fraietta 22 November 2018
%% Modified by Rodrigo Schramm on 22 September 2018
%% Modified by Luke Dahl on 17 October 2-17
%% Modified by Cumhur Erkut on <2016-10-11 Tue>
%% Modified by Edgar Berdahl on 5 November 2014
%% Modified by Baptiste Caramiaux on 25 November 2013
%% Modified by Kyogu Lee on 7 October 2012
%% Modified by Georg Essl on 7 November 2011
%%
%% And here's the template:
%%
%% The first command in your LaTeX source must be the \documentclass
%% command.
%%
%% For submission and review of your manuscript please change the
%% command to \documentclass[manuscript, screen, review]{nimeart}.
%%
%% When submitting camera ready or to TAPS, please change the command
%% to \documentclass[sigconf]{nimeart} or whichever template is required
%% for your publication.
%%
%%
% \documentclass[sigconf]{nimeart}
% \documentclass[sigconf]{nimeart}
\documentclass[sigconf,anonymous,review]{nimeart}
\usepackage{graphicx,subcaption,svg}

@@

% Option 2:
\begin{teaserfigure}
 \centering
  \includegraphics[width=0.58\textwidth]{src/images/49-key-front-top.png}
  \caption{49-key Model Harpsichord Mechanism by \anon{Roberto Livi, Bologna 2024}}
  \Description{An overhead and front view of the replica harpsichord. The overhead view shows the exposed jacks rows, 49 per row and the slant of the bridge and change of sctring from the left to the right.
The front view shows arch detailing on the edge of each key in the same style as is found on early Italian harpsichords.}
  \label{fig:teaser}
\end{teaserfigure}
